---
title: "SurNamExp_usage"
author: "Ayush Pandia"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SurNamExp_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SurNamExp)
```

## About the Package 

- **What it is:** SurNamExp packages a clean surname dataset (last_names) and an interactive Shiny app for quick exploration.
- **Run it fast:** launch with SurNamExp::launch_app() to filter, rank, and summarise names by frequency.
- **Data inside:** last_names has two columns — Surname (character) and Per_1000_Americans (numeric).
- **Reproducible pipeline:** the dataset is built from a script in data-raw/ so you can regenerate and update it.
- **Well-documented:** functions and data use roxygen2 docs; this vignette shows usage and interpretation.
- **Typical workflow:** pick a subset → view plot/table → read summary stats → export or cite the results.
- **Design choice:** keep the Shiny UI thin; put reusable logic in small helper functions for clarity and testing.
- **Install hint:** remotes::install_github("https://github.com/ETC5523-2025/assignment-4-packages-and-shiny-apps-apan0085", upgrade = "never") then launch_app().

